The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-20 src/ms.tex
Correct numpy version that introduces __array_function__

    \astropyQuantity\ is a backbone of \astropy, leveraging the power of
    \package{numpy} and adding units. Previously, many \package{numpy} functions
    would strip a \astropyQuantity\ of its units (or fail outright), limiting
    \astropyQuantity's usefulness. Now, advances in \package{numpy} function
    overloading (see for example
    \href{https://numpy.org/neps/nep-0018-array-function-protocol.html}{NEP 18})
    mean \astropyQuantity\ works with almost all \package{numpy} (version 1.7+)
    functions. These advances have similarly benefitted many
    \package{numpy}-dependent packages, like \package{scipy} and their sparse
    matrices. And again \astropypkg benefits since more \package{scipy}
    functions now work with \astropyQuantity.

>>>>

    \astropyQuantity\ is a backbone of \astropy, leveraging the power of
    \package{numpy} and adding units. Previously, many \package{numpy} functions
    would strip a \astropyQuantity\ of its units (or fail outright), limiting
    \astropyQuantity's usefulness. Now, advances in \package{numpy} function
    overloading (see for example
    \href{https://numpy.org/neps/nep-0018-array-function-protocol.html}{NEP 18})
    mean \astropyQuantity\ works with almost all \package{numpy} (version 1.17+)
    functions. These advances have similarly benefitted many
    \package{numpy}-dependent packages, like \package{scipy} and their sparse
    matrices. And again \astropypkg benefits since more \package{scipy}
    functions now work with \astropyQuantity.
